Post CMOS technologies: An Overview and Analysis

### 2025-06-05 Paper.tex
finished memristor facts

>>>>

\subsubsection{Vector-Matrix Multiplication (VMM) Core}
The central component in the vector-matrix multiplication core 
is the memristor crossbar array. In this array, memrisotrs are placed
at the crosspoints of a grid of wires. Voltages are inputted through
the rows of the wire and the at each cross point the current is 
found through Ohm's Law. Kirchoff's current law then sums up all the 
currents through the vertical beams and the sum of these currents 
is the result of the vector multiplication. Mathematically the
product as a current is 
\[I_j = \Sigma_iV_iG_{ij}.\]

These raw analog values are then fed to a analog to digital converter
(ADC) to then turn into digital magnitudes. Finally, an activation
function (often a sigmoid or ReLU) is applied to these results to 
introduce nonlinearities, making the output resemble various desired 
distributions. 
\begin{figure}[H]
  \centering
  \includegraphics[scale = 0.3]{images/Neural-network-implementation-using-memristor-crossbar-arrays-a-shows-a-conventional.png}
  \caption{Memristor crossbar array}
\end{figure}

\subsubsection{Demonstrations of Memristor Neural Networks}
Notably, the University of Michigan created a memristor based 
computer that utilized a 54x108 memristor crossbar array. 
With this computer they were able to create a single layer perception 
that classified a 5x5 array of pixels, identifying the greek letters 
drawn in the 25 pixel array with 100\% accuracy. In addition, they 
implemented a two layer neural network that found commonalities and 
differences in breast cancer screenings, correctly classifying 
the cases as benign or malignant with 94.6\% accuracy.
%cite here%

\subsection{Challenges to Implementing Memristors}
Despite their demonstrated potential, several critical challenges still
prevent the widespread and practical use of memristors. Among these challenges
the most prominent ones are the lack of reliable manufacturing ability,
resistance drift, and non-linear resistance programming.

Memristors are still unable to be manufactured reliably and the 
the cost of metal alloys is much more than that of silicon. Manufacturing 
metals to these scales is also much harder. These manufactured devices also 
suffer from drift where the programmed resistance can change over time 
to deviations in the environment like temperature. Non-linearities 
in how the resistance is programmed also make it extremely difficult to
program large scale memristor arrays. Supposed identitical memristors 
could require different voltage thresholds or to be applied for varying 
amount of times to program them to have the same resistance.

\subsection{Personal Thoughts}
With the advent of
